### 2022-01-31 README.Rmd
bibfix

---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

@@

The agreed datasets are the final, dataset used in much of the paper and figures. It includes our best efforts at cleaning the data and reconciling intercoder agreement. The dataset is available in long and wide format.
  - [codings_long_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_long_agreed.Rds)
  - [codings_wide_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_wide_agreed.Rds)

@@

### Acknowledgements

>>>>

---
output: 
  github_document:
      toc: true
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
``` 
[![CC BY-NC-SA 4.0][cc-by-nc-sa-shield]][cc-by-nc-sa]

@@

The agreed datasets are the final, dataset used in much of the paper and figures. It includes our best efforts at cleaning the data and reconciling intercoder agreement. The dataset is available in long and wide format.

  - [codings_long_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_long_agreed.Rds)
  - [codings_wide_agreed.Rds](https://github.com/CenterForPeaceAndSecurityStudies/ICBEdataset/blob/master/replication_data/out/codings_wide_agreed.Rds)

@@

### License

This work is licensed under a
[Creative Commons Attribution-NonCommercial-ShareAlike 4.0 International License][cc-by-nc-sa].

[![CC BY-NC-SA 4.0][cc-by-nc-sa-image]][cc-by-nc-sa]

[cc-by-nc-sa]: http://creativecommons.org/licenses/by-nc-sa/4.0/
[cc-by-nc-sa-image]: https://licensebuttons.net/l/by-nc-sa/4.0/88x31.png
[cc-by-nc-sa-shield]: https://img.shields.io/badge/License-CC%20BY--NC--SA%204.0-lightgrey.svg
